%-------------------------
% Resume in LaTeX
% Zachary Lee Kai Yi — Software Engineer / Full Stack / Mobile
%-------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{#1 \vspace{-2pt}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}


%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape \textbf{Lee Kai Yi Zachary}} \\ \vspace{4pt}
    \small
    \faPhone\ +65 8142 2748 \quad
    \faEnvelope\ \href{mailto:lkyzachary@gmail.com}{lkyzachary@gmail.com} \quad
    \faLinkedin\ \href{https://www.linkedin.com/in/zachary-lee-ky/}{linkedin.com/in/zachary-lee-ky} \quad
    \faGlobe\ \href{https://zachyboiii.github.io/zac-portfolio/}{Portfolio}
\end{center}

\vspace{-8pt}
\begin{center}
  \small Software engineer skilled in full-stack web development, native iOS and Android mobile engineering, and production AI systems.
\end{center}

%-----------WORK EXPERIENCE-----------
\section{Work Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {OCBC Bank}{May 2026 -- Aug 2026}
      {AI and Mobile Engineer Intern}{Singapore}
      \resumeItemListStart
        \resumeItem{Maintained the native iOS client of OCBC WoW, an AI avatar banking app for premier private clients (S\$1.5M+ assets under management), shipping UI refinements and stability fixes in Swift to support the app's beta rollout to wealth clients.}
        \resumeItem{Developed FastAPI backend services powering a multi-agent AI system orchestrated with LangGraph, using AWS Bedrock for scalable cloud-native LLM inference, PGVector (PostgreSQL) as the production vector database with ChromaDB for local development, and a Redis caching layer to reduce response latency.}
        \resumeItem{Implemented a wealth portfolio advisory AI agent using Retrieval-Augmented Generation (RAG) over real-time market data spanning 7 indices and commodities, OCBC research, and client portfolio data, alongside AI guardrails and compliance controls aligned with MAS (Monetary Authority of Singapore) financial AI regulations.}
      \resumeItemListEnd

    \resumeSubheading
      {Edgemaker.ai}{Jan 2026 -- May 2026}
      {AI / Full Stack Development Intern}{Singapore}
      \resumeItemListStart
        \resumeItem{Developed and deployed RESTful APIs in Java (Spring Boot) and Node.js integrated with a Next.js frontend for production AI-powered applications, deploying the platform to DigitalOcean with a GitHub Actions CI/CD pipeline for automated releases.}
        \resumeItem{Redesigned the subscription system end-to-end: integrated HitPay's payment API and enforced plan-based feature access with subscription guards in the Spring Boot backend, embedding each plan's blocked features into the JWT for stateless authorisation.}
        \resumeItem{Implemented fuzzy searching with MongoDB search indexes, and built a plug-and-play UI for clients to compose custom workflows from different LLM agents, linking the frontend, backend, and chatbot backend services into a cohesive, user-friendly product.}
      \resumeItemListEnd

    \resumeSubheading
      {Singapore University of Technology and Design (SUTD)}{May 2025 -- Aug 2025}
      {Teaching Assistant — 10.020 Data Driven World}{Singapore}
      \resumeItemListStart
        \resumeItem{Coached two cohorts of 50 students each in Python programming, data manipulation with Pandas/NumPy, and foundational machine learning algorithms through consultations and debugging sessions.}
        \resumeItem{Graded assignments and project deliverables with structured technical feedback, and collaborated with faculty to refine course materials.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, Java, JavaScript, TypeScript, Swift, SQL, HTML/CSS, Tailwind CSS} \\
     \textbf{Frameworks \& Libraries}{: React.js, Next.js, Node.js, Express.js, Spring Boot, FastAPI, Streamlit} \\
     \textbf{Cloud \& Infrastructure}{: AWS Bedrock, DigitalOcean, Docker, Redis, PostgreSQL, MongoDB, Firebase, PGVector, ChromaDB, Hadoop, Apache Spark} \\
     \textbf{Testing \& DevOps}{: Jest, Playwright, Git, GitHub Actions, CI/CD, REST API Design} \\
     \textbf{AI / ML}{: Retrieval-Augmented Generation (RAG), Multi-Agent Systems, LangGraph, LangChain, LLM Fine-tuning, Prompt Engineering, Deep Reinforcement Learning, PyTorch, Scikit-Learn, Pandas, NumPy, Matplotlib} \\
     \textbf{Tools}{: Xcode, Android Studio, Godot Engine, Figma} \\
     \textbf{Methodologies}{: Agile / Scrum, Object-Oriented Programming (OOP), Microservices Architecture} \\
    }}
 \end{itemize}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Singapore University of Technology and Design (SUTD)}{Sep 2023 -- Present}
      {B.Eng. Computer Science and Design — GPA 4.65/5.0 (Honors with Highest Distinction)}{Singapore}
      \resumeItemListStart
        \resumeItem{SUTD Global Distinguished Scholarship Holder.}
        \resumeItem{Relevant coursework: Data Structures \& Algorithms, Machine Learning, Database Systems \& Big Data, Computer Systems Engineering, Information Systems \& Android Programming, Elements of Software Construction.}
      \resumeItemListEnd
    \resumeSubheading
      {University of Waterloo}{Sep 2025 -- Dec 2025}
      {Exchange Program}{Canada}
      \resumeItemListStart
        \resumeItem{Coursework: Introduction to Machine Learning, Introduction to Artificial Intelligence, Human Computer Interactions.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart

    \resumeProjectHeading
      {\textbf{Hotel Booking Platform} $|$ \emph{React.js, Express.js, MongoDB, Jest, Playwright}}{May 2025 -- Aug 2025}
      \resumeItemListStart
        \resumeItem{Built a full-stack hotel booking platform with Ascenda Loyalty integration, featuring lazy loading, real-time filtering, and interactive map visualisation in React.js.}
        \resumeItem{Architected the RESTful Express.js and MongoDB backend with secure authentication and session management; achieved 90\%+ test coverage via Jest and Playwright end-to-end tests.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Vroom — Android Learning Driver App} $|$ \emph{Java, Firebase, Android}}{Jan 2025 -- Apr 2025}
      \resumeItemListStart
        \resumeItem{Engineered an Android application connecting learner drivers with private instructors, featuring real-time booking, scheduling, in-app chat, and interactive quizzes.}
        \resumeItem{Designed scalable MVC architecture using Java OOP principles with Firebase Realtime Database for live booking updates and push notifications.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Storehouse — Volunteer Delivery Management System} $|$ \emph{Node.js, Express.js, PostgreSQL, JavaScript}}{Dec 2025 -- Jan 2026}
      \resumeItemListStart
        \resumeItem{Built RESTful backend services with Node.js and Express.js, implementing full CRUD operations against a PostgreSQL database for volunteer delivery scheduling and management.}
        \resumeItem{Created responsive frontend features in JavaScript and HTML/CSS, including an interactive Google Calendar-style delivery view and dynamic form components.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{TruthieGO} $|$ \emph{Godot Engine, Firebase, NoSQL — DSTA BrainHack 2025 Champion}}{May 2025 -- Jun 2025}
      \resumeItemListStart
        \resumeItem{Won Champion in the CODE\_EXP Competitive Category at DSTA BrainHack 2025 with a 2D educational board game built in Godot Engine and GDScript, engineering modular game logic across multiple game modes and interactive mini-games.}
        \resumeItem{Integrated Firebase (NoSQL) for real-time user authentication, session management, and cross-device progress tracking.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Chess AI Engine} $|$ \emph{Deep Reinforcement Learning, PyTorch, Neural Networks}}{Jan 2026}
      \resumeItemListStart
        \resumeItem{Developed a chess engine in PyTorch, training a neural network through self-play deep reinforcement learning to evaluate board positions and predict move probabilities, reaching an estimated 1500 Elo playing strength.}
        \resumeItem{Built the end-to-end RL training pipeline with policy and value networks, using iterative self-play and experience replay to improve model convergence and playing strength.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------LEADERSHIP AND VOLUNTEERING-----------
\section{Leadership \& Volunteering}
  \resumeSubHeadingListStart

    \resumeSubheading
      {New Creation Church}{Aug 2022 -- Present}
      {Lead IC, Games — Kids Camp Volunteer}{Singapore}
      \resumeItemListStart
        \resumeItem{Led end-to-end planning and execution of game activities for large-scale kids camps with 600+ attendees; managed volunteer teams and liaised with external vendors for logistics and equipment.}
      \resumeItemListEnd

    \resumeSubheading
      {SUTD Freshman Orientation}{May 2024 -- Sep 2024}
      {Orientation Group Leader Head}{}
      \resumeItemListStart
        \resumeItem{Spearheaded event planning and led a team of group leaders, mentoring incoming freshmen through the university-wide orientation programme.}
      \resumeItemListEnd

    \resumeSubheading
      {SUTD Volleyball Club}{Sep 2023 -- Jan 2025}
      {Secretary}{}
      \resumeItemListStart
        \resumeItem{Represented SUTD in Singapore University Games (2023 \& 2024); managed club attendance, logistics, and administrative operations; co-organised inter-club camps with the SUTD Tchoukball Club.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

\end{document}
