%-------------------------
% Resume in LaTeX
% Zachary Lee Kai Yi — AI Engineer
%-------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{#1 \vspace{-2pt}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}


%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape \textbf{Lee Kai Yi Zachary}} \\ \vspace{4pt}
    \small
    \faPhone\ +65 8142 2748 \quad
    \faEnvelope\ \href{mailto:lkyzachary@gmail.com}{lkyzachary@gmail.com} \quad
    \faLinkedin\ \href{https://www.linkedin.com/in/zachary-lee-ky/}{linkedin.com/in/zachary-lee-ky} \quad
    \faGlobe\ \href{https://zachyboiii.github.io/zac-portfolio/}{Portfolio}
\end{center}

\vspace{-8pt}
\begin{center}
  \small AI Engineer skilled in LLM systems, multi-agent orchestration, RAG pipelines, and full-stack development.
\end{center}

%-----------WORK EXPERIENCE-----------
\section{Work Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {OCBC Bank}{May 2026 -- Aug 2026}
      {AI and Mobile Engineer Intern}{Singapore}
      \resumeItemListStart
        \resumeItem{Implemented a wealth portfolio advisory AI agent for OCBC WoW, an AI avatar banking app for premier private clients (S\$1.5M+ assets under management), building Retrieval-Augmented Generation (RAG) pipelines over real-time market data spanning 7 indices and commodities, OCBC research, and client portfolio data to deliver personalised insights 24/7 via voice and text.}
        \resumeItem{Developed backend services for a multi-agent AI system of domain-specialised agents orchestrated with LangGraph and served through FastAPI, using AWS Bedrock for cloud-native LLM inference, PGVector (PostgreSQL) as the production vector database with ChromaDB for local development, and a Redis caching layer to reduce response latency.}
        \resumeItem{Implemented AI guardrails and compliance controls aligned with MAS (Monetary Authority of Singapore) financial AI regulations, and maintained the native iOS client in Swift, shipping UI refinements and stability fixes for the beta rollout to wealth clients.}
      \resumeItemListEnd

    \resumeSubheading
      {Edgemaker.ai}{Jan 2026 -- May 2026}
      {AI / Full Stack Development Intern}{Singapore}
      \resumeItemListStart
        \resumeItem{Built LLM agents for enterprise chatbots — a personal planner agent managing calendars and to-do lists with Google Calendar integration, and a payment agent collecting payments from clients' end-customers through HitPay's API — implementing tool calling for backend data access and inter-agent routing to direct requests to the right domain-specialised agent.}
        \resumeItem{Built a file upload and retrieval agent implementing Retrieval-Augmented Generation (RAG), ingesting user-uploaded files into OpenAI's vector store and retrieving relevant content to ground responses; applied prompt engineering to improve response quality and add guardrails against hallucination.}
        \resumeItem{Developed and deployed the supporting RESTful APIs in Java (Spring Boot) and Node.js, integrated with a Next.js frontend for production AI-powered applications.}
      \resumeItemListEnd

    \resumeSubheading
      {Singapore University of Technology and Design (SUTD)}{May 2025 -- Aug 2025}
      {Teaching Assistant — 10.020 Data Driven World}{Singapore}
      \resumeItemListStart
        \resumeItem{Coached two cohorts of 50 students each in Python programming, data manipulation with Pandas/NumPy, and foundational machine learning algorithms through consultations and debugging sessions.}
        \resumeItem{Graded assignments and project deliverables with structured technical feedback, and collaborated with faculty to refine course materials.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{AI / ML}{: LLM Fine-tuning, Retrieval-Augmented Generation (RAG), Multi-Agent Systems, Tool Calling, LangGraph, LangChain, Prompt Engineering, Deep Reinforcement Learning, PyTorch, Scikit-Learn, Pandas, NumPy, Matplotlib} \\
     \textbf{Cloud \& Infrastructure}{: AWS Bedrock, Docker, Redis, PGVector, ChromaDB, OpenAI Vector Store, PostgreSQL, MongoDB, Firebase, Hadoop, Apache Spark} \\
     \textbf{Languages}{: Python, Java, JavaScript, TypeScript, Swift, SQL, HTML/CSS, Tailwind CSS} \\
     \textbf{Frameworks \& Libraries}{: React.js, Next.js, Node.js, Express.js, Spring Boot, FastAPI, Streamlit} \\
     \textbf{Testing \& DevOps}{: Jest, Playwright, Git, CI/CD, REST API Design} \\
     \textbf{Tools}{: Xcode, Android Studio, Godot Engine, Figma} \\
     \textbf{Methodologies}{: Agile / Scrum, Object-Oriented Programming (OOP), Microservices Architecture} \\
    }}
 \end{itemize}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Singapore University of Technology and Design (SUTD)}{Sep 2023 -- Present}
      {B.Eng. Computer Science and Design — GPA 4.65/5.0 (Honors with Highest Distinction)}{Singapore}
      \resumeItemListStart
        \resumeItem{SUTD Global Distinguished Scholarship Holder.}
        \resumeItem{Relevant coursework: Data Structures \& Algorithms, Machine Learning, Database Systems \& Big Data, Computer Systems Engineering, Information Systems \& Android Programming, Elements of Software Construction.}
      \resumeItemListEnd
    \resumeSubheading
      {University of Waterloo}{Sep 2025 -- Dec 2025}
      {Exchange Program}{Canada}
      \resumeItemListStart
        \resumeItem{Coursework: Introduction to Machine Learning, Introduction to Artificial Intelligence, Human Computer Interactions.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart

    \resumeProjectHeading
      {\textbf{\href{https://zachyboiii.github.io/zac-portfolio/}{zac.ai — In-Browser RAG Portfolio Chatbot}} $|$ \emph{RAG, Transformers.js, React.js, OpenRouter}}{2026}
      \resumeItemListStart
        \resumeItem{Built a Retrieval-Augmented Generation (RAG) chatbot embedded in my portfolio site, deploying a transformer embedding model (all-MiniLM-L6-v2 via Transformers.js/WebAssembly) directly in the browser to perform low-latency cosine-similarity retrieval over a precomputed vector store.}
        \resumeItem{Engineered a build-time embedding pipeline in Node.js that parses my LaTeX resume and site data into knowledge chunks and precomputes their vectors; served streaming LLM responses through the OpenRouter API with automatic multi-model fallback for high availability.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{World Cup Predictor} $|$ \emph{Python, LightGBM, XGBoost, CatBoost, scikit-learn, MLflow}}{Jun 2026}
      \resumeItemListStart
        \resumeItem{Built an ML pipeline that predicts World Cup match outcomes across every tournament stage — full-time result classifier, goals regressors, extra-time and penalty shootout models — benchmarking LightGBM, XGBoost, and CatBoost on 48,000+ historical international matches; correctly predicted the 2026 FIFA World Cup winner.}
        \resumeItem{Engineered a 38-feature vector (Elo ratings, rolling form, head-to-head records, tournament experience) with chronological train/test splits to prevent data leakage and sample weighting to up-rank matches resembling World Cup 2026 conditions; tracked experiments with MLflow.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Chess AI Engine} $|$ \emph{Deep Reinforcement Learning, PyTorch, Neural Networks}}{Jan 2026}
      \resumeItemListStart
        \resumeItem{Developed a chess engine in PyTorch, training a neural network through self-play deep reinforcement learning to evaluate board positions and predict move probabilities, reaching an estimated 1500 Elo playing strength.}
        \resumeItem{Built the end-to-end RL training pipeline with policy and value networks, using iterative self-play and experience replay to improve model convergence and playing strength.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{TruthieGO} $|$ \emph{Godot Engine, Firebase, NoSQL — DSTA BrainHack 2025 Champion}}{May 2025 -- Jun 2025}
      \resumeItemListStart
        \resumeItem{Won Champion in the CODE\_EXP Competitive Category at DSTA BrainHack 2025 with a 2D educational board game built in Godot Engine and GDScript, engineering modular game logic across multiple game modes and interactive mini-games.}
        \resumeItem{Integrated Firebase (NoSQL) for real-time user authentication, session management, and cross-device progress tracking.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Hotel Booking Platform} $|$ \emph{React.js, Express.js, MongoDB, Jest, Playwright}}{May 2025 -- Aug 2025}
      \resumeItemListStart
        \resumeItem{Built a full-stack hotel booking platform with Ascenda Loyalty integration, featuring lazy loading, real-time filtering, and interactive map visualisation in React.js.}
        \resumeItem{Architected the RESTful Express.js and MongoDB backend with secure authentication and session management; achieved 90\%+ test coverage via Jest and Playwright end-to-end tests.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Storehouse — Volunteer Delivery Management System} $|$ \emph{Node.js, Express.js, PostgreSQL, JavaScript}}{Dec 2025 -- Jan 2026}
      \resumeItemListStart
        \resumeItem{Built RESTful backend services with Node.js and Express.js, implementing full CRUD operations against a PostgreSQL database for volunteer delivery scheduling and management.}
        \resumeItem{Created responsive frontend features in JavaScript and HTML/CSS, including an interactive Google Calendar-style delivery view and dynamic form components.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Vroom — Android Learning Driver App} $|$ \emph{Java, Firebase, Android}}{Jan 2025 -- Apr 2025}
      \resumeItemListStart
        \resumeItem{Engineered an Android application connecting learner drivers with private instructors, featuring real-time booking, scheduling, in-app chat, and interactive quizzes.}
        \resumeItem{Designed scalable MVC architecture using Java OOP principles with Firebase Realtime Database for live booking updates and push notifications.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------LEADERSHIP AND VOLUNTEERING-----------
\section{Leadership \& Volunteering}
  \resumeSubHeadingListStart

    \resumeSubheading
      {New Creation Church}{Aug 2022 -- Present}
      {Lead IC, Games — Kids Camp Volunteer}{Singapore}
      \resumeItemListStart
        \resumeItem{Led end-to-end planning and execution of game activities for large-scale kids camps with 600+ attendees; managed volunteer teams and liaised with external vendors for logistics and equipment.}
      \resumeItemListEnd

    \resumeSubheading
      {SUTD Freshman Orientation}{May 2024 -- Sep 2024}
      {Orientation Group Leader Head}{}
      \resumeItemListStart
        \resumeItem{Spearheaded event planning and led a team of group leaders, mentoring incoming freshmen through the university-wide orientation programme.}
      \resumeItemListEnd

    \resumeSubheading
      {SUTD Volleyball Club}{Sep 2023 -- Jan 2025}
      {Secretary}{}
      \resumeItemListStart
        \resumeItem{Represented SUTD in Singapore University Games (2023 \& 2024); managed club attendance, logistics, and administrative operations; co-organised inter-club camps with the SUTD Tchoukball Club.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

\end{document}
